---
title: "Case Study 7"
output: 
  html_document:
    keep_md: TRUE
    code_folding: hide
  
---
**Chance Lister**
```{r}
library(haven)
library(readr)
library(readxl)
library(downloader)
library(measurements)
library(tidyverse)
library(foreign)
```
# Insert/Tidying Worldwide
```{r}
xlsx1 <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Height.xlsx", xlsx1, mode = "wb")

df_ww <- read_xlsx(xlsx1, skip = 2)

view(df_ww)


ww_tidy <- df_ww %>% 
  pivot_longer(c(`1800`:`2011`), names_to = "year_decade", values_to = "height.cm")

view(ww_tidy)

ww_tidy1 <- ww_tidy %>%
  separate(year_decade, into = c("Century", "Decade", "Year"), sep = c(-2,-1), remove = FALSE) 

view(ww_tidy1)

ww_tidy1$year_decade <- as.numeric(ww_tidy1$year_decade)
ww_tidy1$Century <- as.numeric(ww_tidy1$Century)
ww_tidy1$Decade <- as.numeric(ww_tidy1$Decade)
ww_tidy1$Year <- as.numeric(ww_tidy1$Year)

ww_inches <- ww_tidy1 %>% 
  mutate(height.in = conv_unit(height.cm, "cm", "inch"))

ww_inches <- na.omit(ww_inches)

view(ww_inches)

ww_height <- ww_inches[order(ww_inches$year_decade),]

view(ww_height)
```
# Inserting other Data Sets
```{r}
df_ger <- read_dta("https://github.com/WJC-Data-Science/DTS350/raw/master/germanprison.dta")

view(df_ger)

df_ger1 <- read_dta("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/germanconscr.dta")

view(df_ger1)

df_heights <- read_csv("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv")

view(df_heights)

sav <- tempfile()
download("https://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", sav, mode = "wb")
df_sav <- read_sav(sav)

view(df_sav)  

dbf <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Heights_south-east/B6090.DBF", dbf, mode = "wb")
df_dbf <- read.dbf(dbf)

view(df_dbf)
```
# Tidying Data Sets
## Study 1
```{r}
df_1 <- df_ger1 %>% 
  select(bdec, height)

df_1 <- df_1 %>% 
  rename(birth_year = bdec) %>% 
  rename(height.cm = height)

df_1$height.in <- conv_unit(df_1$height.cm, "cm", "inch")


df_1 <- add_column(df_1,study = "germanconscr")

view(df_1)
```
## Study 2
```{r}
df_2 <- df_ger %>% 
  select(bdec, height)

df_2 <- df_2 %>% 
  rename(birth_year = bdec) %>% 
  rename(height.cm = height)

df_2$height.in <- conv_unit(df_2$height.cm, "cm", "inch")


df_2 <- add_column(df_2,study = "german_prison")

view(df_2)
```
## Study 3
```{r}
df_3 <- df_dbf %>% 
  select(SJ, CMETER)

df_3 <- df_3 %>% 
  rename(birth_year = SJ) %>% 
  rename(height.cm = CMETER)


df_3$height.in <- conv_unit(df_3$height.cm, "cm","inch")

df_3 <- add_column(df_3, study = "southeast")

view(df_3)
```
## Study 4
```{r}
df_4 <- df_heights %>% 
  select(height)

df_4 <- df_4 %>% 
  rename(height.in = height)

df_4$height.cm <- conv_unit(df_4$height.in, "inch","cm")

df_4 <- add_column(df_4, birth_year = 1950)
df_4 <- add_column(df_4, study = "BLS")

df_4 <- df_4 %>% 
  select(birth_year, height.cm, height.in, study)

view(df_4)
```
## Study 5
```{r}
df_5 <- df_sav %>% 
  select(DOBY, RT216F, RT216)

df_5 <- df_5 %>% 
  mutate(height.in = ((RT216F*12) + RT216))

df_5 <- df_5 %>% 
  mutate(birth_year = 1900 + DOBY)


df_5  <- add_column(df_5 , study = 'wisconsin')

df_5$height.cm <- conv_unit(df_5$height.in, 'inch', 'cm')

df_5 <- df_5 %>% 
  select(birth_year, height.in, height.cm, study)

view(df_5)
```
# Combinding Data
```{r}
df_tidy <- bind_rows(df_1, df_2, df_3, df_4, df_5)

view(df_5)

setwd("/Users/chancelister/ListerC/ListerC/DTS350TemplateMaster/Week_07/analysis")

saveRDS(ww_height, file = 'ww_height.Rds')
saveRDS(df_tidy, file = 'df_tidy.rds')
```
# Visualizations
```{r}
germany <- ww_height %>% 
  filter(`Continent, Region, Country` == "Germany")
```
# Visulization #1
```{r}
vis_1 <- ggplot() +
  geom_point(data = ww_height, mapping = aes(x = year_decade, y = height.in), color = 'grey') +
  geom_line(data = germany, mapping = aes(x = year_decade, y = height.in), color = 'orange') +
  labs(x = "Year",
       y = "Height (in)",
       title = "Germany Height Over Decades") +
  theme_dark()

vis_1
```

This first visualization represents both the worlwide data set and the germany data set. Germany is the line portion and we see it contniue to rise over time.

# Visualization #2 
```{r}
vis_2 <- ggplot(data = df_tidy) +
  geom_count(mapping = aes(x = birth_year, y = height.in), color = "green") +
  facet_wrap(~study) +
  theme_dark()
  
vis_2
```

The second visualization shows all of the data sets side by side with year on the x axis and height (in) on the y axis. We see little to no trend with this visualization.

# Driving Questions

The first visualization shows that the worldwide trend and germany are both increasing in height over the decades. Whereas my second visualization shows that this does not seem true.